linguistic_analysis_C-D.Rmd : Linguistic quantity and complexity

### 2021-09-16 code/aa-flowers-pilot_analysis.Rmd
add ms analyses

```{r feedback}
d.feedback
d.feedback %>% ggplot(aes(x = human)) + geom_bar(stat = "count") + theme_jmank()
```

@@

[] fix roundId

```{r deference}
trial_deference <- d.by_player_metrics %>% 
  rename(roundID = "_id") %>% 
  full_join(d.contexts %>% 
              select(roundID, blinded, label, utility)) %>%
  filter(blinded != playerId) %>%
  group_by(playerId, roundID) %>%
  summarize(deference = utility[label == playerResponse] != max(utility))

d.deference <- d.by_player_metrics %>% 
  rename(roundID = "_id") %>% 
  left_join(trial_deference)
```

>>>>

```{r feedback}
d.feedback
d.feedback %>% ggplot(aes(x = human)) + geom_bar(stat = "count")
```

@@

```{r deference}
trial_deference <- d.by_player_metrics %>% 
  full_join(d.contexts %>% 
              select(roundId, blinded, label, utility)) %>%
  filter(blinded != playerId) %>%
  group_by(playerId, roundId) %>%
  summarize(deference = utility[label == playerResponse] != max(utility))

d.deference <- d.by_player_metrics %>% 
  left_join(trial_deference)
```

### 2021-09-16 code/aa_mic_submission_analyses.Rmd
add ms analyses

```{r setup}
library(here)
library(tidyverse)

@@

For the purposes of this ms, we're removing all unfinished games from the analyses 
```{r}
n_players = 3
n_rounds = 24
games_exclude <- d.rounds %>% group_by(gameId) %>% tally() %>% filter(n!=n_players*n_rounds) %>% select(gameId)

d.rounds.final <-  d.rounds %>% 
  left_join(d.games %>% select(gameId, conditionName, condition)) %>% 
  filter(conditionName != "coopCartel") %>% 
  mutate(game_complete = !(gameId %in% games_exclude$gameId))

d.raw_chat.final <- d.raw_chat %>% 
  left_join(d.games %>% select(gameId, conditionName, condition)) %>% 
  mutate(game_complete = !(gameId %in% games_exclude$gameId)) 
```

# Summary Stats
## Game counts
```{r}
d.games %>% 
  mutate(game_complete = !(gameId %in% games_exclude$gameId)) %>%
  group_by(-game_complete, condition, chatEnabled) %>%
  count()
```

## Game lengths
## Bonus Payments

# Points x Time x Num. Words

# Avg. Points Per Round

# Language Reduction

# Georgia Analyses

>>>>

```{r}
library(here)
library(tidyverse)

@@

For the purposes of this ms, we're removing all unfinished games from the analyses 
```{r}
n_players = 3
n_rounds = 24

game_completion <- d.rounds %>% 
  group_by(gameId) %>% 
  tally() %>% 
  mutate(game_complete = n==n_players*n_rounds) %>%
  rename(n_trials = n)

d.games.final <- d.games %>% 
  left_join(game_completion) %>% 
  replace_na(list(game_complete = FALSE, n_trials = 0))

d.games.conditions <- d.games.final %>% 
  select(gameId, color, condition, chatEnabled, game_complete) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"))

d.rounds.final <-  d.rounds %>% 
  left_join(d.games.final %>% 
              select(gameId, conditionName, condition,color, chatEnabled, game_complete)) %>% 
  filter(conditionName != "coopCartel",
         game_complete)

d.raw_chat.final <- d.raw_chat %>% 
  left_join(d.games.final %>% 
              select(gameId, conditionName, condition, game_complete)) %>%
  filter(game_complete)

```

# Summary Stats
## Game counts
```{r}
d.games.final %>% 
  group_by(-game_complete, condition, chatEnabled) %>%
  count()
```

## Game lengths
```{r}
d.games.final %>% 
filter(game_complete) %>%
  group_by(condition, chatEnabled) %>%
  mutate(gameLength_minutes = gameLength/60) %>%
  summarize_at("gameLength_minutes", funs(min, max, mean))
```

## Bonus Payments
Max bonus payment
```{r}
max(d.players$bonus, na.rm=T)
```
## Hourly compensation 
```{r}
#I just pulled these averages from prolific
(35.81*16 + 25.75 * 47 + 26.38 * 47 + 24.76*18 + 10.17* 18 + 12.64 * 18 + 11.79 * 68 + 11.24*66)/(16+47+47+18+18+18+68+66)

```

# Summarizing Data

We'll pull out the summary statistics with 3 views: 
* by player (points earned, number of utterances, number of words)
  ** selection metrics: select hidden, non-top flower
* by round (group points earned, max possible points earned in round, number of words exchanged by group)
* by game (total points, max possible points in game)

```{r}
#player language per round
d.player_word_counts <- d.raw_chat.final %>% 
  filter(type == "message") %>%
  mutate(text = gsub('[[:punct:] ]+',' ',text),
         text = str_squish(text),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+") + 1) %>% 
  group_by(gameId, blockNum, trialNum, repNum, playerId, numPlayers) %>%
  summarize(text = paste0(text, collapse = ' - '),
            total_num_words = sum(utt_length_words),
            total_num_chars = sum(utt_length_chars))

# player points per round
d.by_player_metrics <- d.rounds.final  %>% 
  left_join(d.player_word_counts) %>%
  left_join(d.games.conditions) %>% 
  replace_na(list(total_num_words = 0, total_num_chars = 0))

#add deference measure and flower ranking
deference_rank <-  d.by_player_metrics %>%  
  full_join(d.contexts %>% 
              select(roundId, blinded, label, utility)) %>%
  filter(blinded != playerId) %>%
  group_by(playerId, roundId) %>%
  arrange(-utility) %>%
  mutate(selectionRank = c(0:3)) %>%
  filter(playerResponse == label) %>%
  mutate(deference = selectionRank != 1) %>%
  select(roundId, playerId,deference, selectionRank)

d.by_player_metrics <- d.by_player_metrics %>% 
  left_join(d.contexts %>% select(roundId, playerResponse = label, 
                                  selectedHidden = blinded,
                                  selectionUtility = utility)) %>%
  mutate(selectedHidden = selectedHidden == playerId) %>%
  left_join(deference_rank)
```

Calculate the best possible per round

```{r max_round}
d.max_round <- d.contexts %>%
  group_by(gameId, repNum, blockNum, trialNum) %>%
  #top 3 flowers
  slice_max(utility, n = 3) %>%
  summarise(roundMax = sum(utility))
```

```{r}
d.by_round_metrics <- d.by_player_metrics  %>% 
  group_by(gameId, trialNum, roundId) %>%
  summarize(roundUtility = sum(playerUtility, na.rm = T),
            numWords = sum(total_num_words, na.rm = T),
            numChars = sum(total_num_chars, na.rm = T),
            numFlowers = n_distinct(playerResponse),
            roundLength = max(time_sec)) %>%
  left_join(d.max_round) %>%
  mutate(pointsAdjusted = roundUtility/roundMax) %>% 
  left_join(d.games.conditions)
```
```{r}
d.by_game_metrics <- d.by_round_metrics  %>% 
  group_by(gameId) %>%
  summarize(gameUtility = sum(roundUtility, na.rm = T),
            numWords = sum(numWords, na.rm = T),
            numChars = sum(numChars, na.rm = T),
            maxPossPoints = sum(roundMax)) %>%
  mutate(pointsAdjusted = gameUtility/maxPossPoints) %>% 
  left_join(d.games.conditions) %>%
  left_join(d.games.final %>% select(gameId, gameLength))
```

# Merge in RL Experiments

```{r read-rl}
d.rl_metrics <- read_csv(here("data/processed_data/RL_experiment_results.csv"))

#get in line with player summary statistics?

d.rl.player_metrics <- d.rl_metrics %>% 
  mutate(gameId = paste(condition_raw, languageConditionRaw, trial, sep = "-"), 
         playerId = paste0(trial, "-",agent)) %>%
  select(playerId, languageCondition, condition, avgPlayerPoints = reward) %>% 
  mutate(rl_agent = "Agent")

```

# Fig 1 & 2
## RL Point Comp

### All Players
```{r}
d.by_player_metrics %>%
  group_by(languageCondition, condition, playerId) %>%
  summarize(avgPlayerPoints = mean(playerUtility)) %>% 
  mutate(rl_agent = "Human") %>%
  rbind(d.rl.player_metrics) %>%
  ggplot(aes(x = condition, y = avgPlayerPoints, color = rl_agent)) + 
  geom_point(position=position_jitterdodge(dodge.width=.5, jitter.width = .1), alpha = .25) +
  stat_summary(fun.data = "mean_cl_boot", position=position_dodge(width=.5)) + 
  scale_color_brewer(palette="Dark2")+ theme_jmank() + 
  facet_wrap(~languageCondition)+ 
  theme(legend.position = "bottom", axis.title.x=element_blank()) +
  labs(y = "Average Player Points", color = "Player Type")
```
### Avg Points over game
Do the same but by average points per round across players

```{r}
d.rl.game_metrics <- d.rl_metrics %>% 
  mutate(gameId = paste(condition_raw, languageConditionRaw, trial, sep = "-"), 
         playerId = paste0(trial, "-",agent)) %>%
  group_by(gameId, languageCondition, condition) %>% 
  summarize(avgRoundPoints = sum(reward)) %>%
  mutate(rl_agent = "Agent")

d.rl.game_metrics
```

{} to match other plot, facet by utility condition, color by agent type?
```{r}
rl_comparison <- d.by_round_metrics %>%
  group_by(languageCondition, condition, gameId) %>%
  summarize(avgRoundPoints = mean(roundUtility)) %>% 
  mutate(rl_agent = "Human") %>%
  rbind(d.rl.game_metrics) %>%
  ggplot(aes(x = languageCondition, y = avgRoundPoints, color = condition)) + 
  geom_point(position=position_jitterdodge(dodge.width=.5, jitter.width = .1), alpha = .25) +
  stat_summary(fun.data = "mean_cl_boot", position=position_dodge(width=.5)) + 
  scale_color_bay()+ theme_jmank() + 
 # labs(y = "Average Points", color = "Player Type") +
  labs(y = "Average Points per Round", x = "Language Condition", color = "Utility Condition") +
  facet_wrap(~rl_agent)+ 
  theme(legend.position = "bottom")

rl_comparison
```
```{r}
d.by_round_metrics %>%
  group_by(languageCondition, condition, gameId) %>%
  summarize(avgRoundPoints = mean(roundUtility)) %>% 
  mutate(rl_agent = "Human") %>%
  rbind(d.rl.game_metrics) %>%
  ggplot(aes(x = languageCondition, y = avgRoundPoints, color = condition)) + 
  geom_point(position=position_jitterdodge(dodge.width=.5, jitter.width = .1), alpha = .25) +
  stat_summary(fun.data = "mean_cl_boot", position=position_dodge(width=.5)) + 
  scale_color_brewer(palette="Dark2")+ theme_jmank() + 
 # labs(y = "Average Points", color = "Player Type") +
  labs(y = "Average Points per Round", color = "Player Type", x = "Language Condition") +
  facet_wrap(~rl_agent)+ 
  theme(legend.position = "bottom")
```

## Points x Time x Num. Words
```{r}
lang_by_points <- d.by_game_metrics %>% 
  ggplot(aes(x = gameLength/60, y = gameUtility, shape = languageCondition, color = log(numWords))) + 
  geom_point(alpha = .8) +
  geom_smooth(aes(group = condition), method=lm, formula=y~log(x),color = "black")+
  facet_grid(cols = vars(condition)) + 
  labs(x = "Game length (in Minutes)", 
       y = "Points Earned by Group",
       color = "Log N. Words",
       shape = "Language") + 
  theme_jmank() +  scale_color_steps(low = "#edd746", high = "#6B9555") + theme(legend.position = "bottom")
lang_by_points
```

### Rewards Blurb

```{r}
d.by_game_metrics %>% mutate(lang_used = numWords > 0) %>%
  group_by(languageCondition, lang_used) %>% count()

max(d.by_game_metrics$numWords)
```
# Language Reduction
Want number of words exchanged over the game
 More utterances in individual, (same turns)

 shared utilities

 more questions in shared?
```{r}
lang_reduction <- d.by_round_metrics %>%
  filter(languageCondition == "Lang") %>%
  ggplot(aes(x = trialNum, y = numWords, color = condition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  #geom_smooth(method=lm, formula=y~log(x))+
   labs(x = "Trial Number", y = "N. Words", color = "Utility Condition")+ 
  scale_color_bay() + theme_jmank() +theme(legend.position = "bottom")# + scale_y_continuous(trans='log10')

utterances <- d.raw_chat.final %>% 
  left_join(d.games.conditions) %>%
  filter(type == "message") %>%
  select(gameId, trialNum, playerId, text) %>%
  #this drops the NAs, we want to keep instances where there was a selection but no message ugh
  mutate(text = gsub('[[\']+]|[[:punct:] ]+',' ',text),
         text = str_squish(text),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+")+1) %>%
  group_by(gameId, trialNum, playerId) %>%
  summarize(utt_length_chars = list(utt_length_chars),
            utt_length_words = list(utt_length_words))

expand_utt <- d.raw_chat.final %>%
  select(gameId, trialNum, playerId) %>% 
  distinct() %>%
  full_join(utterances)

no_lang_index <- sapply(expand_utt$utt_length_chars, is.null)
expand_utt$utt_length_chars[no_lang_index] <- 0
expand_utt$utt_length_words[no_lang_index] <- 0

utt_reduction <- expand_utt %>% 
  unnest(cols = c(utt_length_chars, utt_length_words)) %>%
  left_join(d.games.conditions) %>%
  filter(languageCondition == "Lang", game_complete) %>%
  group_by(gameId, trialNum, languageCondition, condition) %>%
  summarize(mean_utt_length = mean(utt_length_words))

utt_reduction %>%  ggplot(aes(x = trialNum+1, y = mean_utt_length, color = condition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  labs(x = "Trial Number", y = "Average N. Words per Utterance", color = "Utility Condition")+ 
  scale_color_bay() + theme_jmank() +theme(legend.position = "bottom")

#points increase as language decreases?
d.by_round_metrics %>%
  filter(languageCondition == "Lang") %>%
  ggplot(aes(x = trialNum, y = roundUtility, color = condition)) + 
  geom_point(alpha = .5) + 
  geom_smooth(method=lm)+
  scale_color_bay() + theme_jmank()

```

# Final Figs

```{r}
library(patchwork)
lang_by_points
rl_comparison
lang_reduction

lang_by_points + lang_reduction +plot_annotation(tag_levels = 'A')#, labels = c('A', 'B'), label_size = 12, aligh = "hv")

ggsave(here(fig_path, "points_earned_reduction_joined.png"), height = 4, width = 11)

rl_comparison
ggsave(here(fig_path, "rl_comparison.png"), height = 3, width = 5)
```

# Number of questions
Adapted from Georgia's report

```{r}
question_words <- c("who",  "what",  "where",  "why",  "how")
d_messages <- d.raw_chat.final %>% 
  filter(type=="message") %>%
  filter(!is.na(text))

d_messages <- d_messages %>% 
  mutate(question_mark = ifelse(str_detect(text, "\\?"),TRUE,FALSE),
         question_word = grepl(paste(question_words, collapse="|"), tolower(text)),
         any_question = ifelse((question_mark | question_word), TRUE, FALSE))

d_messaged_summarized <- d_messages %>% group_by(gameId, trialNum, condition) %>% 
  summarize(total_utt = n(), 
            n_question_marks = sum(question_mark), 
            n_question_words = sum(question_word),
            n_questions = sum(any_question),
            proportion_q = n_question_marks/total_utt)

d_messaged_summarized %>%
  ggplot(aes(x = trialNum, y = proportion_q, color = condition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  #geom_smooth(method=lm, formula=y~log(x))+
   labs(x = "Trial Number", y = "Prop of Questions", color = "Utility Condition")+ 
  scale_color_bay() + theme_jmank() + theme(legend.position = "none") + ggtitle("All Trials")

```

### 2021-09-16 code/linguistic_analysis_C-D.Rmd
add ms analyses

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(here)
library("stringr")
library(Hmisc)
library("spacyr")
library(ggrepel)
library(cowplot)
library(grid)
library(gridExtra)

source("./theme_specs.R")
```

@@

```{r main data, include=TRUE}
d<- read_csv("../data/processed_data/joined_data/filtered_raw_chat.csv")
d_flowers <- d %>% 
  filter(type=="message") %>%
  filter(!is.na(text))

@@

ggplot(d_flowers_utt_length_trial, aes(x=trialNum, y=total_num_words,  color=condition))+
#  facet_grid(rows =vars(condition)) +
  geom_point()+
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Total number of words", x="Trial number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("Number of words per trial")

ggplot(d_flowers_utt_length_trial, aes(x=trialNum, y=mlu,  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="Mean Length of Utterance", y="MLU", x="Trial number")+
  theme_jmank() + scale_color_bay() + theme(legend.position="bottom") #+ 
  #theme(text = element_text(size = 30))

@@

#jpeg("~/Desktop/plots/nword_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_utt_length_rep, aes(x=repNum, y=log(mlu+1),  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="MLU", y="MLU", x="Rep number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("MLU per rep")#+
 # theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nturn_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_n_turns_trial, aes(x=trialNum, y=n,  color=condition))+
  #facet_grid(rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Trial number")+
  theme(legend.position="bottom") + 
  theme_bw() +
  ggtitle("Number of turns per trial")#+
  #theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nturn_block.jpg", width = 950, height = 950)
ggplot(d_flowers_n_turns_block, aes(x=blockNum, y=n,  color=condition))+
 # facet_grid(rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Block number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() + theme(legend.position = "bottom")
  ggtitle("Number of turns per block")#+
 # theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nutts_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_n_utt_speaker, 
       aes(x=trialNum, y=n_utt_speaker,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
 # facet_grid(~condition) +
  xlab("Trial number") + 
  ylab("Number of utterances") + 
  theme_bw()#+
 # theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nutts_block.jpg", width = 950, height = 950)
ggplot(d_flowers_n_utt_speaker, 
       aes(x=blockNum, y=n_utt_speaker,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
 # facet_grid(~condition) +
  xlab("Block number") + 
  ylab("Number of utterances") + 
  theme_bw()#+
#  theme(text = element_text(size = 30))
#dev.off()

@@

turnb_function <- function(d_flowers_n_utt_speaker, c, q) {
  p<-ggplot2::ggplot(d_flowers_n_utt_speaker, aes(y=n_utt_speaker, x=trialNum, label=gameId, color=condition)) + xlim(c,q) +
  geom_point(alpha = .5)+
  geom_smooth(method = "lm", formula = y~x)+
  xlab("Trial number") + 
  theme_bw()+
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
return(p)
}

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
a<- turnb_function(d_flowers_n_utt_speaker %>% filter(blockNum==0), 0,5) + ylab("Number of utterances")+  theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank())+ labs(subtitle = "Block1")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
b<- turnb_function(d_flowers_n_utt_speaker %>% filter(blockNum==1), 6,11) +  theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank(),axis.text.y = element_blank())+ labs(subtitle = "Block2")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
c<- turnb_function(d_flowers_n_utt_speaker %>% filter(blockNum==2), 12,17) +  theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank(),axis.text.y = element_blank())+ labs(subtitle = "Block3")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
d<- turnb_function(d_flowers_n_utt_speaker %>% filter(blockNum==3), 18,23) +theme(legend.position="none",axis.title.y = element_blank(),axis.title.x = element_blank(),axis.text.y = element_blank())+ labs(subtitle = "Block4")

@@

### Parts of speech
```{r pos, eval=TRUE, include=TRUE}

@@

 text <- d_flowers$text
 parsed <- spacy_parse(text,pos=TRUE) %>%
   select(doc_id, pos) %>%
   group_by(doc_id) %>%
   mutate(pos = paste(pos, collapse=",")) %>%
   distinct()
#   
# d_flowers_pos  <- cbind(d_flowers, parsed) %>%
#   separate_rows(pos, convert = TRUE) %>%
#   group_by(condition, blockNum, gameId, pos) %>%
 #  filter(pos=="NOUN"| pos=="VERB") %>% #| pos=="ADJ"| pos=="ADP"| pos=="DET" | pos=="PRON") %>%
  # summarise(pos_count=n()) %>%
  # left_join(d_flowers_uttlength_block) %>%
  # mutate(prop_pos=pos_count/total_num_words)

@@

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_ttr_trial, 
       aes(x=trialNum, y=ttr_,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
 # facet_grid(rows =vars(condition)) +
  xlab("Trial number") + 
  ylab("Type_token ratio") + 
  ylim(0,1)+
  theme_bw()+
  ggtitle("TTR per trial")#+
 # theme(text = element_text(size = 30))
#dev.off()

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)

library(here)
library("stringr")
library(Hmisc)
library("spacyr")
library(ggrepel)
library(cowplot)
library(grid)
library(gridExtra)
library(tidyverse)
source("./theme_specs.R")
```

@@

```{r main data, include=TRUE}
d<- read_csv("../data/processed_data/joined_data/filtered_raw_chat.csv")
d_flowers <- d %>% 
  filter(type=="message") %>%
  filter(!is.na(text)) 
```

@@

ggplot(d_flowers_utt_length_trial, aes(x=trialNum, y=total_num_words,  color=condition))+
#  facet_grid(rows =vars(condition)) +
  geom_point(alpha = .25)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Total number of words", x="Trial number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("Number of words per trial")

ggplot(d_flowers_utt_length_trial, aes(x=trialNum, y=mlu,  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.25)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="Mean Length of Utterance", y="MLU", x="Trial number")+
  theme_jmank() + scale_color_bay() + theme(legend.position="bottom") #+ 
  #theme(text = element_text(size = 30))

@@

#rep num is irrelevant here?
#jpeg("~/Desktop/plots/nword_rep.jpg", width = 950, height = 950)
ggplot(d_flowers_utt_length_rep, aes(x=repNum, y=log(mlu+1),  color=condition))+
#  facet_grid( rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
 # scale_y_continuous(limits = c(0,15))+
  labs(title="MLU", y="MLU", x="Rep number")+
  theme(legend.position="bottom") + 
  theme_jmank() + scale_color_bay() +
  ggtitle("MLU per rep")#+
 # theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nturn_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_n_turns_trial, aes(x=trialNum, y=n,  color=condition))+
  #facet_grid(rows =vars(condition)) +
  geom_jitter(alpha=.25)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Trial number")+
  theme(legend.position="bottom") + 
  scale_color_bay() +
  theme_jmank() +
  ggtitle("Number of turns per trial")#+
  #theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nturn_block.jpg", width = 950, height = 950)
ggplot(d_flowers_n_turns_block, aes(x=blockNum, y=n,  color=condition))+
 # facet_grid(rows =vars(condition)) +
  geom_jitter(alpha=.05)+
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of turns", y="Number of turns", x="Block number")+
  theme_jmank() + scale_color_bay() + theme(legend.position = "bottom")+
  ggtitle("Number of turns per block")#+
 # theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nutts_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_n_utt_speaker, 
       aes(x=trialNum, y=n_utt_speaker,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.25) +
 # facet_grid(~condition) +
  xlab("Trial number") + 
  ylab("Number of utterances") + 
  theme_jmank() + scale_color_bay() + theme(legend.position = "bottom")
 # theme(text = element_text(size = 30))
#dev.off()

@@

#jpeg("~/Desktop/plots/nutts_block.jpg", width = 950, height = 950)
ggplot(d_flowers_n_utt_speaker, 
       aes(x=blockNum, y=n_utt_speaker,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.1) +
 # facet_grid(~condition) +
  xlab("Block number") + 
  ylab("Number of utterances") + 
  theme_jmank() + scale_color_bay() + theme(legend.position = "bottom")
#  theme(text = element_text(size = 30))
#dev.off()

@@

turnb_function <- function(d_flowers_n_utt_speaker, c, q) {
  p<-ggplot2::ggplot(d_flowers_n_utt_speaker, aes(y=n_utt_speaker, x=trialNum, label=gameId, color=condition)) + xlim(c,q) +
  geom_point(alpha = .5)+
  geom_smooth(method = "lm", formula = y~x)+
  xlab("Trial number") + 
theme_jmank() + scale_color_bay() +  
    theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
return(p)
}

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
a<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==0), 0,5) + 
  ylab("Number of utterances")+  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank())+ labs(subtitle = "Block1")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
b<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==1), 6,11) +  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank())+ 
  labs(subtitle = "Block2")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
c<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==2), 12,17) +  
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank())+ 
  labs(subtitle = "Block3")

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
d<- turnb_function(d_flowers_n_utt_speaker %>% 
                     filter(blockNum==3), 18,23) +
  theme(legend.position="none",axis.title.y = element_blank(),
        axis.title.x = element_blank(),axis.text.y = element_blank())+ 
  labs(subtitle = "Block4")

@@

#TODO I dont really understand why this figure is done this way?
```

### Parts of speech
```{r pos, eval=FALSE, include=FALSE}

@@

 text <- d_flowers$text
 #I dont have spacy in an env for this project, cant reproduce will have to add later -jm TODO
 # parsed <- spacy_parse(text,pos=TRUE) %>%
 #   select(doc_id, pos) %>%
 #   group_by(doc_id) %>%
 #   mutate(pos = paste(pos, collapse=",")) %>%
 #   distinct()
#   
# d_flowers_pos  <- cbind(d_flowers, parsed) %>%
#   separate_rows(pos, convert = TRUE) %>%
#   group_by(condition, blockNum, gameId, pos) %>%
 #  filter(pos=="NOUN"| pos=="VERB") %>% #| pos=="ADJ"| pos=="ADP"| pos=="DET" | pos=="PRON") %>%
  # summarise(pos_count=n()) %>%
  # left_join(d_flowers_uttlength_block) %>%
  # mutate(prop_pos=pos_count/total_num_words)

@@

#jpeg("~/Desktop/plots/ttr_trial.jpg", width = 950, height = 950)
ggplot(d_flowers_ttr_trial, 
       aes(x=trialNum, y=ttr_,  color=condition)) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_point(alpha=.05) +
 # facet_grid(rows =vars(condition)) +
  xlab("Trial Number") + 
  ylab("Type to Token Ratio (TTR)") + 
  ylim(0,1)+
  scale_color_bay() + theme_jmank() +
  theme(legend.position = "bottom")
 # theme(text = element_text(size = 30))
#dev.off()

ggsave(here(fig_path, "ttr_trials.png"), height = 3, width = 3)
